Embodied Neuromorphic Benchmarks

### 2015-08-15 paper/paper.tex
Added discussion and conclusion

\subsection{Online and offline learning}

@@

We can also use this sort of benchmark to examine the effects of various
parameters in the model.  For example, in Figure \ref{fig:analysis_delay_cpu}
we show what happens as the delays $t_q$ and $t_u$ are increased.
Importantly, the range on these parameters is larger than before ($U(0, 0.04)$
rather than $U(0, 0.01)$).  This shows that if the delay is short (less than 0.02), the controller performs well, and if it is very large (greater than 0.03),
the controller performs poorly.  However, for delays between 0.02 and 0.03,
the controller will sometimes perform well and sometimes perform poorly.  The
difference is due to the other random parameters in the system.  Interestingly,
running this same benchmark on SpiNNaker in Figure \ref{fig:analysis_delay_spinn} shows that SpiNNaker actually performs better on this
task.  Further analysis is needed to determine exactly why this is.

@@

\section{Other Benchmarks}

(sketch out how this approach could be applied to other task)

Adaptive Jacobian

Driving down a corridor, avoiding obstacles

Classical conditioning

Operant conditioning

@@

- And then a concluding thing pointing out that we've now defined N benchmarks, each of which looks at different aspects of the hardware. If people have new hardware that is good in particular situations, they can adjust the core benchmark be specifying different parameter distributions. This lets people be explicit about what their hardware is good at, while still using the same basic benchmark framework.

@@

\section*{Acknowledgments}
Text Text Text Text Text Text  Text Text Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text. Text Text Text Text Text Text  Text Text Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text.

>>>>

\subsection{Online and Offline Learning}

@@

We can also use this sort of benchmark to examine the effects of various
parameters in the model.  For example, in Figure \ref{fig:analysis_delay_cpu}
we show what happens as the delays $t_q$ and $t_u$ are increased.
Importantly, the range on these parameters is larger than before ($U(0, 0.04)$
rather than $U(0, 0.01)$).  This shows that if the delay is short (less than 0.02), the controller performs well, and if it is very large (greater than 0.03),
the controller performs poorly.  However, for delays between 0.02 and 0.03,
the controller will sometimes perform well and sometimes perform poorly.  The
difference is due to the other random parameters in the system.  Interestingly,
running this same benchmark on SpiNNaker in Figure \ref{fig:analysis_delay_spinn} shows that SpiNNaker actually performs better on this
task.  This is somewhat surprising, as we are currently using the slow
Ethernet interface to SpiNNaker, rather than the high-speed I/O system that
is meant for motor control.  Further analysis is needed to determine exactly why this is.

@@

\section{Discussion}

The benchmarks described above all use the same underlying minimal simulation
as a way to characterize the overall performance of particular hardware
across a range of situations.  By adjusting the random distributions that
define that range of situations, we generate different benchmarks that
explore the capabilities of the systems in different ways.  This allows for
an explicit depiction of the sorts of conditions in which particular
neuromorphic hardware perfroms well.  After all, it is unlikely that one
piece of neuromorphic hardware will be the best choice in all situations;
rather, these benchmarks allow us to demonstrate the advantages and disadvantages
of the hardware by looking at the same underlying system, but with multiple
different distributions of parameters.

Python software for the minimal simulation and the full benchmarks are
available at \texttt{http://github.com/ctn-waterloo/ctn_benchmarks}.

\subsection{Benchmark Improvements}

The benchmarks presented here can be improved and further developed in many
ways.  Most obviously, we need to benchmark more hardware, and in particular
we would most like to consider analog neuromorphic hardware.  Interestingly, these
benchmarks can also be run on software simulations of proposed hardware.

However, it is also clear that performance these benchmarks is a result of
a combination of the hardware itself, the algorithm being run, and the system that
interfaces the hardware to the environment.  Thus, for any given hardware, 
we can explore improvements to the algorithm (better choices for $e$, 
different learning rules, adaptive learning rates, adapting $K_p$ and $K_d$, etc.).
For example, in the SpiNNaker hardware implementation not only can the neuron model
be adjusted, but the distribution of the task across the multiple cores is also
under programmer control.  Futhermore, SpiNNaker provides a custom I/O interface
for high-speed communication that could be used to reduce communication delay.

In addition, we would like to clarify and expand the space of physical tasks
being approximated by the minimal simulation.  To do this, we will use the
previously discussed method to 
calibrate the model across a variety of different physical systems.  Of
particular interest will be the space of random external force functions that
are randomly generated.  Right now, this is a simple set of randomly
generated vectors with a few common nonlinearities.  However, if we can
identify classes of tasks that we are likely to want to control, we can
create minimal simulations across those sorts of tasks.  For example, it
would be possible to randomly generate $N$-joint arms with random arm
lengths and random masses, and derive (an approximation of) the actual forces 
that would be seen in that situation.  However, when doing this careful
consideration would be needed to make sure that the randomly generated simulated arm
had motors powerful enough to lift itself against gravity.

\subsection{Other Benchmarks}

The approach to benchmarking presented here can also be applied to other tasks,
defining minimal simulations and evaluating hardware across a random sampling
of that space.

The most straightforward expansion would be to consider motor control where
the state being controlled \emph{is not the motor state itself}.  That is,
suppose we want to control the position of a hand $x$, but our output $u$
only directly controls the joints $q$ of an arm.  The position of the hand $x$
is some function of $q$, but this function may be unknown or highly complex.
Crucially, there is a learning rule that is similar to the one discussed above
that can learn this mapping (\citealt{adaptiveJacobian}), and we have had
some success in using it for particular arm control tasks (citealt{dewolf2014}).
This would give a benchmark with a much more flexible set of capabilities;
for example a non-neural version of this learning algorithm was able to
learn to control a robot arm to follow a certain path, given only the
visual feedback of where the tip of its hand was, without knowing the
geometry of its own hand or the position of the camera with relation to that
hand (\citealt{adaptiveJacobian}).  While it is unlikely that such a
system would work for \emph{any} possible sensorimotor combination, developing
such a benchmark could identify the space of such embodiments that a
particular algorithm running on particular neuromorphic hardware would be
good at controlling.

We also believe this approach to developing benchmarks would be applicable
to more complex and abstract tasks.  For example, much of the original work
on minimal simulation involved robot navigation and obstacle avoidance.  
\cite{Jakobi97evolutonaryrobotics} created a
minimal simulation of an environment with fixed walls, a mobile robot, and
various sensory systems.  A benchmark involving movement between locations
while avoiding collisions could be defined, and the environment could be
enhanced with moving obstacles and a richer set of sensors.  The eventual
goal would be to achieve reliable movement in an environment that includes
people.

Another direction to take this sort of benchmark would be classical and
operant conditioning.  This sort of learning is extremely common in living
creatures, and is vital for dealing with novel environments.  As such,
it is natural to define tasks involving learning the associates between
sensory events in the environment (akin to classical conditioning) and the
associations between actions and desired sensory states (akin to operant
conditioning).  Again, the approach of minimal simulation could be used
to generate random complex sensory mappings, and various neuromorphic
learning algorithms could be evaluated in terms of their ability to
discern these patterns.  Importantly, this would also include the ability
to unlearn these patterns as the environment changes.  Interestingly, the
neuron-based classical conditioning learning rule used by \cite{verschure2003}
is quite similar to the learning rule used in the adaptive control benchmark
here.

@@

The primary purpose of this paper is to describe a new method for benchmarking
neuromorphic hardware that addresses the problem of reliably benchmarking
in a complex task that involves interaction with an environment.  This
method involves building a ``minimal'' simulation; one that is extremely
simple in terms of required computation, but that has a high degree of
adjustable variability.  By benchmarking across that whole space of
possibilities, we can identify hardware that performs well across that whole
space, and is thus likely to be useful in real-world situations.  In order
to identify what real-world situations are covered by a minimal simulation,
we can calibrate the variability in that simulation with particular physical
systems.

We demonstrated this approach by defining a minimal simulation and a task
based around adaptive motor control.  We presented a basic algorithm that
can use neuromorphic hardware to improve performance on this task.  While this
algorithm can be run on a variety of hardware, other algorithms could also
be used on this task, and there are many implementation possibilities.
Importantly, by measuring performance while adjusting the distributions of
parameters in the benchmark, it is possible to characterize different aspects
of the hardware, identifying how different aspects of the task affect
performance for different hardware.  This was demonstrated by providing
five different benchmarks, each based on the same minimal simulation, but
setting parameters in different ways.  We believe this sort of flexibility
is important in a benchmark, as it lets researchers be explicit about what
their hardware is good at, while still using the same basic and shareable
benchmark framework.

@@

\section*{Acknowledgments}

Text Text Text Text Text Text  Text Text Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text. Text Text Text Text Text Text  Text Text Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text.
